\documentclass[11pt]{article}
\usepackage[margin=4em]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{blindtext}
\usepackage{libertine}
\setmonofont{inconsolata}

%\usepackage[T1]{fontenc}
%\usepackage{fontspec}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=6pt,parsep=1pt,partopsep=0pt}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{10pt}{1em}

%\titleformat{\section}{\vspace{1em}}{\thesection.}{0.5em}{\vspace{0pt}}[{\titlerule[0.1pt]}]
%\titleformat{\subsection}{\it}{\thesubsection.}{0.5em}{\vspace{-0.5em}}[]
\setlength\parindent{0pt}
\pagestyle{empty}

%\setmainfont{CMU Concrete}

\begin{document}
{\Huge Wenqi He} \quad \texttt{github.com/galmungral}

\section*{Experience}

\textbf{National Center for Supercomputing Applications}, Urbana, IL, US\\
\textit{Graduate Research Assistant (Research Software Engineering), Visual Analytics Group \hfill Aug. 2022 - Present}
\begin{itemize}
\item Developed software for researchers, focusing on biomedical and geospatial data visualization.
\item Created interactive cartographic visualizations using OpenLayers and GeoJSON.
\item Participated in the maintenance of PhyloDiver, a visualization tool for tumor phylogenies.
\end{itemize}

\textbf{Gllue Software}, Shanghai, China\\
\textit{Front-end Software Engineer, Applicant Tracking System (ATS) \hfill Nov. 2020 - Nov. 2021}
\begin{itemize}
\item Collaborated with multiple teams to build web applications, WeChat mini-programs and libraries.
\item Participated in the maintenance of the user interface builder that powers the customizable ATS.
\item Responsible for the front-end integration of a revamped Single Sign-On system for multiple products.
\end{itemize}

\textbf{Étude LLC}, Atlanta, GA, US\\
\textit{Software Engineer, Founding Team \hfill Aug. 2019 - Aug. 2020}
\begin{itemize}
\item Developed several main features of the NLP-powered PDF reader, including a table of contents parser.
\end{itemize}

\section*{Education}
\textbf{University of Illinois Urbana-Champaign}, Urbana–Champaign, IL, US \hfill \textit{Aug. 2022 - Present} \\
\textit{Master of Computer Science}  \hfill GPA: 4.0/4.0 
\begin{itemize}
\small
\item Formal Semantics / Programming Language Design (K Framework), Compiler Construction (LLVM)
\item Scientific Visualization, Interactive Computer Graphics (WebGL), Computational Photography
\item Distributed Algorithms/Systems, Information Retrieval, Natural Language Processing (PyTorch)
\end{itemize}

\textbf{Georgia Institute of Technology}, Atlanta, GA, US \hfill \textit{Aug. 2015 - Dec. 2019}\\
\textit{Bachelor of Science in Computer Science, Minor in Physics, \textit{summa cum laude}} \hfill GPA: 3.97/4.0\\
\textit{Concentration: Modeling-Simulation and Information Internetworks} \hfill Major GPA: 4.0/4.0
\begin{itemize}
\small
\item Differential Geometry, Partial/Ordinary Differential Equations, Numerical Analysis, Computer Simulation
\end{itemize}

\section*{Personal Projects}
\href{https://github.com/galmungral/particle-simulation}{\textit{A Visualization/Simulation of Particle Collisions}} \hfill (WebGL, Rust, WebAssembly) \\
\href{https://github.com/galmungral/rasterizer}{\textit{A Basic Software Rasterizer for Browsers}} \hfill (C++, Emscripten, WebAssembly) \\
\href{https://github.com/galmungral/mercator}{\textit{A Simple Raster Map Tile Renderer}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/michelangelo}{\textit{Layout Algorithms for Canvas-based User Interface}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/text2svg}{\textit{A Simple Text Renderer}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/telescope}{\textit{A Split SOCKS Proxy for Internet Censorship Circumvention}} \hfill (C, libuv) \\
\href{https://github.com/galmungral/react-teletype}{\textit{An Interactive Server-side React Renderer}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/replay}{\textit{A Front-end Framework and a Module Bundler Built from Scratch}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/hanbun-lang}{\textit{An Esoteric Programming Language Based on Classical Chinese}} \hfill (PureScript) \\
\href{https://github.com/galmungral/sketchpad}{\textit{A Toy Compiler for a Hypothetical Architecture}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/plato}{\textit{A Toy Search Engine Based on the Query Likelihood Model}} \hfill (Python) \\
\href{https://github.com/galmungral/json-crdt}{\textit{A Practical Implementation of Conflict-free Replicated JSON}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/turing-machine}{\textit{A Simulation of the Universal Turing Machine}} \hfill (Haskell, Common Lisp)

\end{document}
