\documentclass[11pt]{article}
\pagestyle{empty}
\setlength\parindent{0pt}

\usepackage[margin=40pt]{geometry}

\usepackage{libertine}
\setmonofont{inconsolata}

\usepackage{enumitem}
\setitemize{itemsep=2pt, parsep=0pt, topsep=0pt, leftmargin=2em}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{16pt}{4pt}
\titlespacing{\subsection}{0pt}{16pt}{2pt}

\usepackage{hyperref}

\begin{document} 
\centering

\begin{minipage}{250pt}
{\Huge\bf Wenqi He}

\vspace{10pt}
\texttt{\href{https://linkedin.com/in/galmungral}{linkedin.com/in/galmungral}\\
\href{https://github.com/galmungral}{github.com/galmungral}\\
\href{mailto:hewenqi96@gmail.com}{hewenqi96@gmail.com}
}


\section*{\sc Education}

\subsection*{University of Illinois Urbana-Champaign}
\textit{Master of Computer Science}\\
Dec. 2023 (expected) \,|\, Urbana, IL, US

\subsection*{Georgia Institute of Technology}
\textit{Bachelor of Science in Computer Science}\\
\textit{Minor in Physics}\\
Dec. 2019 \,|\, Atlanta, GA, US

\section*{\sc Personal Projects}

\href{https://github.com/galmungral/polyrender}{GPU-accelerated Vector Graphics Renderer}\\
\href{https://github.com/galmungral/rasterizer}{Simple Software Rasterizer}\\
\href{https://github.com/galmungral/simple-raytracer}{Simple Software Raytracer}\\
\href{https://github.com/galmungral/mercator}{Simple Raster Map Tile Renderer}\\
\href{https://github.com/galmungral/michelangelo}{Canvas-based User Interface Framework}\\
\href{https://github.com/galmungral/react-teletype}{Server-side Interactive React Renderer} \\
\href{https://github.com/galmungral/replay}{Frontend Framework and Module Bundler}\\
\href{https://github.com/galmungral/hanbun-lang}{Stack-oriented Esoteric Programming Language}


\section*{\sc Relevant Coursework}
\subsection*{\it \S\ Graphics, Physics \& Scientific Computing}
Scientific Visualization\\
Interactive Computer Graphics\\
Computational Photography\\
Parallel Computing (GPU)\\
Numerical Analysis/Methods\\
Partial Differential Equations\\
Differential Geometry\\
General Relativity\\
Quantum Mechanics\\
Quantum Computing

\subsection*{\it \S\ Language, Data \& Communication}
Compiler Construction\\
Relational Databases\\
Distributed Algorithms/Systems\\
Computer Networking\\
Information Security\\
Information Retrieval\\
Natural Language Processing

\end{minipage}
\begin{minipage}{280pt}

\section*{\sc Work Experience}

\subsection*{National Center for Supercomputing Applications}
\textit{Graduate Research Assistant, Visual Analytics} \\
Aug. 2022 - Present \,|\, Urbana, IL, US\\
\begin{itemize}
\item Developed software for scientific researchers, focusing on biomedical and geospatial data visualization.
\item Responsible for the full-stack development and deployment of the BiteMap application for the \href{https://medical-entomology.inhs.illinois.edu/}{INHS MEL}.
\item Created cartographic visualization of tick bite data using GeoJSON, OpenLayers, PostgreSQL and census data.
\item Participated in the maintenance of PhyloDiver, an interactive tool for visualizing tumor phylogenies.
\end{itemize}

\subsection*{Gllue Software}
\textit{Frontend Engineer, Applicant Tracking System (ATS)}\\
Nov. 2020 - Nov. 2021 \,|\, Shanghai, China\\
\begin{itemize}
\item Collaborated with multiple teams to build web applications, WeChat mini-programs, services and libraries.
\item Contributed to the drag-and-drop user interface builder framework that powers the ATS customization system.
\item Responsible for the frontend integration of a new Single Sign-On system for multiple products.
\end{itemize}

\subsection*{Étude LLC}
\textit{Software Engineer, Founding Team}\\
Aug. 2019 - Aug. 2020 \,|\,  Atlanta, GA, US\\
\begin{itemize}
\item Implemented several features of the desktop PDF reader, including table of contents parsing and text highlighting.
\end{itemize}

\section*{\sc Technical Skills}
\subsection*{\it\S\ Languages}
TypeScript, JavaScript, C, C++, GLSL, WebAssumbly, Rust,\\
SQL, Python, Java, PHP, HTML, SVG, CSS, Sass, LESS,\\
OCaml, Haskell, Common Lisp, MATLAB, Mathematica

\subsection*{\it\S\ Frameworks \& Libraries}
Angular, React, Node.js, Next.js, NumPy, SciPy, PyTorch

\subsection*{\it\S\ Development Tools}
Bash, Git, Vim, Visual Studio Code, LLVM, Make,\\
esbuild, Babel, Rollup, webpack, Vite, Tailwind CSS,\\
Puppeteer, Cypress, Jest, TypeDoc, ESLint, Prettier, \\
GitHub Actions, GitLab CI, Docker, Kubernetes

\end{minipage}

\end{document}
