\documentclass[11pt]{article}
\pagestyle{empty}
\setlength\parindent{0pt}

\usepackage[margin=40pt]{geometry}

\usepackage{libertine}
\setmonofont{inconsolata}

\usepackage{enumitem}
\setitemize{itemsep=2pt, parsep=0pt, topsep=0pt, leftmargin=2em}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{20pt}{4pt}
\titlespacing{\subsection}{0pt}{20pt}{2pt}

\usepackage{hyperref}

\begin{document} 
\centering

\begin{minipage}{250pt}
{\Huge\bf Wenqi He}

\vspace{10pt}
\texttt{\href{https://linkedin.com/in/galmungral}{linkedin.com/in/galmungral}\\
\href{https://github.com/galmungral}{github.com/galmungral}\\
\href{mailto:hewenqi96@gmail.com}{hewenqi96@gmail.com}
}

\section*{\sc Education}

\subsection*{University of Illinois Urbana-Champaign}
\textit{Master of Computer Science}\\
Dec. 2023 (expected) \,|\, Urbana, IL, US

\subsection*{Georgia Institute of Technology}
\textit{Bachelor of Science in Computer Science}\\
\textit{Minor in Physics}\\
Dec. 2019 \,|\, Atlanta, GA, US

\section*{\sc Personal Projects}

GPU-accelerated 2D Vector Graphics Renderer\\
Simple Software Rasterizer and Raytracer\\
Simple Vector and Raster Map Tile Renderer\\
Canvas-based User Interface Framework\\
Stack-oriented Esoteric Programming Language\\
Frontend Framework and Module Bundler\\
Server-side Interactive React Renderer

\section*{\sc Relevant Coursework}
\subsection*{\it Graphics \& Scientific Computing}
Scientific Visualization\\
Interactive Computer Graphics\\
Computational Photography\\
GPU Parallel Computing\\
Numerical Analysis/Methods\\
Partial Differential Equations\\
Differential Geometry\\
General Relativity

\subsection*{\it Language \& Communication}
Compiler Construction\\
Relational Databases\\
Distributed Algorithms/Systems\\
Computer Networking\\
Information Security\\
Information Retrieval\\
Natural Language Processing

\end{minipage}
\begin{minipage}{280pt}

\section*{\sc Work Experience}

\subsection*{National Center for Supercomputing Applications}
\textit{Graduate Research Assistant, Visual Analytics} \\
Aug. 2022 - Present \,|\, Urbana, IL, US\\
\begin{itemize}
\item Developed web applications for diverse research projects, with a focus on visualizing geospatial and biomedical data.
\item Created geographic visualizations for various datasets using MapLibre GL JS, OpenLayers, GeoJSON, and PostGIS.
\item Contributed to the maintenance of PhyloDiver, a web-based interactive tool for visualizing tumor phylogenies.
\end{itemize}

\subsection*{Gllue Software}
\textit{Frontend Engineer, Applicant Tracking System (ATS)}\\
Nov. 2020 - Nov. 2021 \,|\, Shanghai, China\\
\begin{itemize}
\item Collaborated with multiple teams to develop web applications, WeChat mini-programs, services, and libraries.
\item Contributed to the drag-and-drop user interface builder framework that powers the ATS customization system.
\item Led the frontend implementation and integration of a new Single Sign-On system across multiple product lines.
\end{itemize}

\subsection*{Étude LLC}
\textit{Software Engineer, Founding Team}\\
Aug. 2019 - Aug. 2020 \,|\,  Atlanta, GA, US\\
\begin{itemize}
\item Implemented several features of the desktop PDF reader, including table of contents parsing and text highlighting.
\end{itemize}

\section*{\sc Technical Skills}
\subsection*{\it Languages}
TypeScript, JavaScript, C, C++, GLSL, WebAssumbly, Rust,\\
SQL, Python, Java, PHP, HTML, SVG, CSS, Sass, LESS,\\
OCaml, Haskell, Common Lisp, MATLAB, Mathematica

\subsection*{\it Frameworks \& Libraries}
Angular, React, Node.js, Next.js, NumPy, SciPy, PyTorch

\subsection*{\it Development Tools}
Bash, Git, Vim, Visual Studio Code, LLVM, Make,\\
esbuild, Babel, Rollup, webpack, Vite, Tailwind CSS,\\
Puppeteer, Cypress, Jest, TypeDoc, ESLint, Prettier, \\
GitHub Actions, GitLab CI, Docker, Kubernetes

\end{minipage}

\end{document}
