\documentclass[12pt]{article}
\usepackage[margin=4em]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{blindtext}
\usepackage{libertine}
\setmonofont{inconsolata}
\usepackage{xeCJK}

%\usepackage[T1]{fontenc}
%\usepackage{fontspec}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=6pt,parsep=1pt,partopsep=0pt}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{10pt}{1em}

%\titleformat{\section}{\vspace{1em}}{\thesection.}{0.5em}{\vspace{0pt}}[{\titlerule[0.1pt]}]
%\titleformat{\subsection}{\it}{\thesubsection.}{0.5em}{\vspace{-0.5em}}[]
\setlength\parindent{0pt}
\pagestyle{empty}

%\setmainfont{CMU Concrete}

\begin{document}
{\Huge Wenqi He} \quad \texttt{github.com/galmungral}

\section*{Experience}

\textbf{美国国家超级计算机应用中心}, Urbana, IL, US\\
\textit{研究生科研助理 (科研软件开发), 可视化分析组, 视觉部门} \hfill Aug. 2022 - Present
\begin{itemize}
\item Developed software for researchers, focusing on biomedical and geospatial data visualization.
\item Created interactive cartographic visualizations using OpenLayers and GeoJSON.
\item Participated in the maintenance of PhyloDiver, a visualization tool for tumor phylogenies.
\end{itemize}

\textbf{谷露软件}, Shanghai, China\\
\textit{前端工程师, ATS (申请人追踪系统)} \hfill Nov. 2020 - Nov. 2021
\begin{itemize}
\item Collaborated with multiple teams to build web applications, WeChat mini-programs and libraries.
\item Participated in the maintenance of the user interface builder that powers the customizable ATS.
\item Responsible for the front-end integration of a revamped Single Sign-On system for multiple products.
\end{itemize}

\textbf{Étude LLC}, Atlanta, GA, US\\
\textit{软件工程师, 创始团队} \hfill Aug. 2019 - Aug. 2020
\begin{itemize}
\item Developed several main features of the NLP-powered PDF reader, including a table of contents parser.
\end{itemize}

\section*{Education}
\textbf{University of Illinois Urbana-Champaign}, Urbana–Champaign, IL, US \hfill Aug. 2022 - Dec. 2023 \\
\textit{计算机科学硕士 (MCS)}  \hfill GPA: 4.0/4.0 
\begin{itemize}
\small
\item 形式语义学/编程语言设计 (K Framework), 编译器构建 (LLVM)
\item 交互式/实时计算机图形学 (WebGL), 科学可视化, 计算摄影学
\end{itemize}

\textbf{Georgia Institute of Technology}, Atlanta, GA, US \hfill Aug. 2015 - Dec. 2019\\
\textit{计算机科学理学学士 (BSCS, \textit{summa cum laude})} \hfill GPA: 3.97/4.0\\
\textit{专修: 建模仿真与网际互联, 辅修: 物理学} \hfill 专业 GPA: 4.0/4.0
\begin{itemize}
\small
\item 经典微分几何, 偏/常微分方程, 数值分析, 计算机模拟, 广义相对论
\end{itemize}

\section*{Personal Projects}
\href{https://galmungral.github.io/mercator}{\textit{简易栅格地图瓦片渲染器}} \hfill (TypeScript) \\
\href{https://galmungral.github.io/particle-simulation}{\textit{简易粒子碰撞模拟/可视化}} 
\hfill (WebGL, Rust, WebAssembly) \\
\href{https://galmungral.github.io/terrain-generator}{\textit{简易3D地形生成器}} \hfill (WebGL, Rust, WebAssembly) \\
\href{https://galmungral.github.io/rasterizer?file=billboard.txt}{\textit{简易3D软件栅格化器}} \hfill (C++, Emscripten, WebAssembly) \\
\href{https://galmungral.github.io/text2svg}{\textit{简易OpenType/TrueType字体渲染器}} \hfill (TypeScript) \\
\href{https://galmungral.github.io/michelangelo}{\textit{基于Canvas的简易 UI 框架/布局系统}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/react-teletype}{\textit{服务端交互式 React 渲染器}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/replay}{\textit{简易前端框架与模块打包器}} \hfill (TypeScript) \\
\href{https://galmungral.github.io/hanbun-lang}{\textit{基于文言的深奥(esoteric)编程语言}} \hfill (PureScript) \\
\href{https://github.com/galmungral/json-crdt}{\textit{JSON式无冲突复制数据类型(CRDT)的一种实用性实现}} \hfill (TypeScript) \\
\href{https://github.com/galmungral/telescope}{\textit{用以规避互联网审查的分离式SOCKS代理}} \hfill (C, libuv) \\
\href{https://github.com/galmungral/plato}{\textit{基于查询似然模型的简易搜索引擎}} \hfill (Python) \\
\href{https://github.com/galmungral/turing-machine}{\textit{通用图灵机的模拟}} \hfill (Haskell, Common Lisp)
\end{document}
